Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

\begin{lemma} \label{lmm:hv}
    Equipped with the algorithm $\A$ described above, the H-V $k$-SJ problem can be solved in time
    \myeqn{
        O(k) \cdot \big( F_{k-1}(n, \out) + n\log n + k \cdot \out \big) \nn
    }
    where $n$ (resp., $\out$) is the input (resp., output) size of the problem. Furthermore, if $\A$ is comparison-based, so is the H-V $k$-SJ algorithm.
\end{lemma}

@@

    \item {{\bf Type 2:}} either $h$ or $v$ fails to cross at least one rectangle in $\set{r_1, r_2, ..., r_{k-2}}$. Equivalently,
    there exists at least a rectangle $r_i$ (for some $i \in [k-2]$) that covers an endpoint of either $h$ or $v$ or both.
}
Figure~\ref{fig:hv:types} illustrates a result tuple of each type, assuming $k = 4$. In Section~\ref{sec:hv:type1} (resp., \ref{sec:hv:type2}), we will explain how to produce the result tuples of Type 1 (resp., 2) in the time complexity claimed in Lemma~\ref{lmm:hv}.

\extraspacing {\bf Remark.} In \cite{rdr+11}, Rahul et al.\ studied the problem of storing a set $H$ of horizontal segments and a set $V$ of vertical segments in a data structure such that, given a query rectangle $r$, all the pairs $(h, v) \in H \times V$ satisfying $h \cap v \cap r \ne \emptyset$ can be reported efficiently. They developed a structure of $O(n \log n)$ space that can be built in $O(n \log n)$ time, and can be used to answer a query in $O(\log n + K)$ time, where $n = |H| + |V|$ and $K$ is the number of pairs reported. Their structure can be utilized to solve H-V 3-SJ in $O(n \log n + \out)$ time. Another structure with the same guarantees can be found in \cite{oa19}. We are unaware of a way to extend their solution to handle H-V $k$-SJ of $k > 3$. Our method for proving Lemma~\ref{lmm:hv} is based on fundamentally different ideas even for $k = 3$.

>>>>

\begin{lemma} \label{lmm:hv}
    Equipped with the algorithm $\A$ described above, the H-V $k$-SJ problem can be solved in
    \myeqn{
        O(k) \cdot \big( F_{k-1}(n, \out) + n\log n + k \cdot \out \big) \nn
    }
    time where $n$ (resp., $\out$) is the input (resp., output) size of the problem. Furthermore, if $\A$ is comparison-based, the H-V $k$-SJ algorithm obtained is also comparison-based.
\end{lemma}

@@

    \item {{\bf Type 2:}} either $h$ or $v$ fails to cross at least one rectangle in $\set{r_1, r_2, ..., r_{k-2}}$. Equivalently,
    at least a rectangle $r_i$ (for some $i \in [k-2]$) covers an endpoint of either $h$ or $v$ or both.
}
Figure~\ref{fig:hv:types} illustrates a result tuple of each type, assuming $k = 4$. In Section~\ref{sec:hv:type1} (resp., \ref{sec:hv:type2}), we will explain how to produce the result tuples of Type 1 (resp., 2) in the time complexity claimed in Lemma~\ref{lmm:hv}.

\extraspacing {\bf Remark.} In \cite{rdr+11}, Rahul et al.\ studied the problem of storing a set $H$ of horizontal segments and a set $V$ of vertical segments in a data structure such that, given a query rectangle $r$, all the pairs $(h, v) \in H \times V$ satisfying $h \cap v \cap r \ne \emptyset$ can be reported efficiently. They developed a structure of $O(n \log n)$ space that can be built in $O(n \log n)$ time, and can be used to answer a query in $O(\log n + K)$ time, where $n = |H| + |V|$ and $K$ is the number of pairs reported. Their structure can be utilized to solve H-V 3-SJ in $O(n \log n + \out)$ time. Oh and Ahn \cite{oa19} developed a structure for a more general version of the problem; in the specific scenario of \cite{rdr+11}, the structure of \cite{oa19} matches the performance guarantees of \cite{rdr+11}. We are unaware of a way to extend their solution to handle H-V $k$-SJ of $k > 3$. Our method for proving Lemma~\ref{lmm:hv} is based on fundamentally different ideas even for $k = 3$.
